quollr: An R Package for Visualizing 2-D Models from Nonlinear Dimension Reductions in High-Dimensional Space

### 2025-12-08 paper-quollr.Rmd
Fixed Figure 10

error_plt <- shared_df |>
  ggplot(aes(x=sqrt_row_wise_total_error, y = density)) +
  geom_point(colour = point_colours[1]) +
  xlab(expression(e[hj])) +
  ylab("") +
  theme_bw() +
  theme(
    #aspect.ratio = 1,
    plot.background = element_rect(fill = 'transparent', colour = NA),
    plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
    panel.background = element_rect(fill = 'transparent',
                                    colour = NA),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(), axis.title.y = element_blank(),
    axis.text.x = element_blank(), axis.ticks.x = element_blank(),
    axis.text.y = element_blank(), axis.ticks.y = element_blank()
  )

error_plt <- ggplotly(error_plt, width = 200,
                      height = 200, tooltip = "none") |>
  style(unselected=list(marker=list(opacity=1))) |>
  highlight(on="plotly_selected", off="plotly_deselect") |>
  config(displayModeBar = FALSE)

nldr_plt <- shared_df |>
  ggplot(aes(x = emb1, y = emb2)) +
  geom_point(alpha=0.5, colour=point_colours[1], size = 0.5) +
  theme_linedraw() +
  theme(
    #aspect.ratio = 1,
    plot.background = element_rect(fill = 'transparent', colour = NA),
    plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
    panel.background = element_rect(fill = 'transparent',
                                    colour = NA),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(), axis.title.y = element_blank(),
    axis.text.x = element_blank(), axis.ticks.x = element_blank(),
    axis.text.y = element_blank(), axis.ticks.y = element_blank()
  )

nldr_plt <- ggplotly(nldr_plt, width = 200,
                     height = 200, tooltip = "none") |>
  style(unselected=list(marker=list(opacity=1))) |>
  highlight(on="plotly_selected", off="plotly_deselect") |>
  config(displayModeBar = FALSE)
```

@@

detourr_output <- detour(
  shared_df,
  tour_aes(
    projection = starts_with("x"),
    colour = type
  )
) |>
  tour_path(grand_tour(2), 
                    max_bases=50, fps = 60) |>
  show_scatter(axes = TRUE, size = 1, alpha = 0.8, 
               edges = as.matrix(trimesh[, c("from_reindexed", "to_reindexed")]),
               palette = c("#66B2CC", "#FF7755"),
                width = "200px", height = "200px")

erlndet_link <- crosstalk::bscols(
    htmltools::div(
        style = "display: grid; grid-template-columns: 1fr 1fr 1fr;
    gap: 0px;
    align-items: start;
    justify-items: center;
    margin: 0;
    padding: 0;",
        error_plt, 
        nldr_plt, 
    htmltools::div(style = "margin-top: 20px;", detourr_output)
    ),
    device = "xs"
)

>>>>

error_plt <- plot_ly(
    shared_df,
    x = ~sqrt_row_wise_total_error, y = ~density,
    type = "scatter",
    mode = "markers",
    marker = list(
        color = point_colours[1],
        size = 3,
        opacity = 0.5
    ),
    hoverinfo = "none"
) |>
    layout(
        width = 250,
        height = 250,
        xaxis = list(
            title = "",
            showgrid = FALSE,
            zeroline = FALSE,
            showticklabels = FALSE,
            ticks = "",
            linecolor = "black",
            mirror = TRUE
        ),
        yaxis = list(
            title = "",
            showgrid = FALSE,
            zeroline = FALSE,
            showticklabels = FALSE,
            ticks = "",
            linecolor = "black",
            mirror = TRUE
        ),
        margin = list(l = 20, r = 20, t = 20, b = 20),
        dragmode = "select"
    ) |> 
    style(selected   = list(marker = list(opacity = 1)), unselected=list(marker=list(opacity=1))) |>
    highlight(on="plotly_selected", off="plotly_deselect") |>
    config(displayModeBar = FALSE)

nldr_plt <- plot_ly(
    shared_df,
    x = ~emb1, y = ~emb2,
    type = "scatter",
    mode = "markers",
    marker = list(
        color = point_colours[1],
        size = 3,
        opacity = 0.5
    ),
    hoverinfo = "none"
) |>
    layout(
        width = 250,
        height = 250,
        xaxis = list(
            title = "",
            showgrid = FALSE,
            zeroline = FALSE,
            showticklabels = FALSE,
            ticks = "",
            linecolor = "black",
            mirror = TRUE
        ),
        yaxis = list(
            title = "",
            showgrid = FALSE,
            zeroline = FALSE,
            showticklabels = FALSE,
            ticks = "",
            linecolor = "black",
            mirror = TRUE
        ),
        margin = list(l = 20, r = 20, t = 20, b = 20),
        dragmode = "select"
    ) |> 
    style(selected   = list(marker = list(opacity = 1)), unselected=list(marker=list(opacity=1))) |>
    highlight(on="plotly_selected", off="plotly_deselect") |>
    config(displayModeBar = FALSE)
```

@@

detourr_output <- detour(
  shared_df,
  tour_aes(
    projection = starts_with("x"),
    colour = type
  )
) |>
  tour_path(grand_tour(2), 
                    max_bases=50, fps = 60) |>
  show_scatter(axes = TRUE, size = 0.5, alpha = 0.8, 
               edges = as.matrix(trimesh[, c("from_reindexed", "to_reindexed")]),
               palette = c("#66B2CC", "#FF7755"),
                width = "250px", height = "250px")

erlndet_link <- crosstalk::bscols(
    htmltools::div(
        style = "display: grid; grid-template-columns: 1fr 1fr 1fr;
    gap: 0px;
    align-items: start;
    justify-items: center;
    margin: 0;
    padding: 0;
    height: 300px;
    width: 400px;",
        error_plt, 
        nldr_plt, 
    htmltools::div(style = "margin-top: 20px;", detourr_output)
    ),
    device = "xs"
)

### 2025-12-08 paper-quollr.tex
Fixed Figure 10

\begin{verbatim}
detourr_output <- detour(
  shared_df,
  tour_aes(
    projection = starts_with("x"),
    colour = type
  )
) |>
  tour_path(grand_tour(2), 
                    max_bases=50, fps = 60) |>
  show_scatter(axes = TRUE, size = 1, alpha = 0.8, 
               edges = as.matrix(trimesh[, c("from_reindexed", "to_reindexed")]),
               palette = c("#66B2CC", "#FF7755"),
                width = "200px", height = "200px")

erlndet_link <- crosstalk::bscols(
    htmltools::div(
        style = "display: grid; grid-template-columns: 1fr 1fr 1fr;
    gap: 0px;
    align-items: start;
    justify-items: center;
    margin: 0;
    padding: 0;",
        error_plt, 
        nldr_plt, 
    htmltools::div(style = "margin-top: 20px;", detourr_output)
    ),
    device = "xs"
)

>>>>

\begin{verbatim}
detourr_output <- detour(
  shared_df,
  tour_aes(
    projection = starts_with("x"),
    colour = type
  )
) |>
  tour_path(grand_tour(2), 
                    max_bases=50, fps = 60) |>
  show_scatter(axes = TRUE, size = 0.5, alpha = 0.8, 
               edges = as.matrix(trimesh[, c("from_reindexed", "to_reindexed")]),
               palette = c("#66B2CC", "#FF7755"),
                width = "250px", height = "250px")

erlndet_link <- crosstalk::bscols(
    htmltools::div(
        style = "display: grid; grid-template-columns: 1fr 1fr 1fr;
    gap: 0px;
    align-items: start;
    justify-items: center;
    margin: 0;
    padding: 0;
    height: 300px;
    width: 400px;",
        error_plt, 
        nldr_plt, 
    htmltools::div(style = "margin-top: 20px;", detourr_output)
    ),
    device = "xs"
)
